---
title: "Reprod. Research. Peer assignm. 2"
author: "Pedro Carmona"
date: "Monday, November 17, 2014"
output: html_document
---


```{r}
temp <- tempfile()
download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2"
              ,temp)
data <- read.table(file=bzfile(temp, "repdata-data-StormData.csv")
                    , header = T
                    , sep = ","
                    , na.strings = c("NA", ""))
unlink(temp)
```

```{r}
str(data)
```

```{r}
number.na <- sapply(data, function(x) sum(is.na(x)))
```

```{r}
which(number.na >= 0.3*nrow(data))
```

```{r}
new.data <- data[,-c(10,11,15,17,18,21,26,28,31,36)]
```

```{r}
new.data <- na.omit(new.data)
```

fata <- table(new.data$EVTYPE,new.data$FATALITIES)
injur <- table(new.data$EVTYPE, new.data$INJURIES)

table(new.data$FATALITIES)

table(new.data$EVTYPE, new.data$STATE)

head(fata)
head(injur)

max.values <- apply(fata,1,which.max)
which.max(max.values)


max.values2 <- apply(fata[-72,],1,which.max)
which.max(max.values2)




  
You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
